Approximation as Differentiation

### 2025-07-08 main/approx-as-tangents.tex
berry78 -> berry79.

In light of the \exref{non-stable-function}, we turn to
\citet{berry78}'s definition of \emph{stable function} that requires
the existence of a reverse mapping directly, even without assuming
that any meets exist:

@@

We have seen that \citet{berry78}'s theory of stable functions between suitable partial orders can be seen as form of differentiability with forward and reverse derivatives. In the next section, we describe a model based on these ideas suitable for constructing executable models of total higher order languages.

>>>>

In light of the \exref{non-stable-function}, we turn to
\citet{berry79}'s definition of \emph{stable function} that requires
the existence of a reverse mapping directly, even without assuming
that any meets exist:

@@

We have seen that \citet{berry79}'s theory of stable functions between suitable partial orders can be seen as form of differentiability with forward and reverse derivatives. In the next section, we describe a model based on these ideas suitable for constructing executable models of total higher order languages.
